\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-02 paper.tex
Rewrite section 2

@@

\section{From human-robot interaction to a deliberative architecture}

@@

Figure~\ref{fig|archi} gives an overview of resulting
architecture~\cite{Alami2011}. An active knowledge base, conveniently thought
as a \emph{semantic blackboard}, connects most of the modules together: the
\emph{geometric reasoning} module (called {\sc Spark}) produces symbolic
assertions describing the dynamics of the robot's environment. These logical
statements are stored in the knowledge base, and reused by the language
processing module (called {\sc Dialogs}), the symbolic task planner (HATP) and
the execution controllers. The output of the language processing module, or the
activities started by the robot controller are likewise stored as symbolic
statements.

Incoming statements may in turn trigger events in the system, which
allow reactive behaviours. These mechanisms are illustrated in the coming
sections.

\begin{figure*}
        \centering

  %%% ORO
  \node at (0,0)[skill, ultra thick, fill=LimeGreen!50] (oro) {Symbolic facts \\ and beliefs management};

  %%% HATP
  \node at (-6, 2)[skill, fill=PineGreen!50] (hatp) {Human-aware symbolic \\ task planning};

  %%% DIALOGS
  \node at (-6, -2) [skill, fill=BrickRed!50] (dialogs) {Dialogue processing};

  %%% SPARK
  \node at (4,-3)[skill, fill=Purple!50] (spark) {%
      \begin{tikzpicture}
        \node at (0,0) (geom) {Geometric \& Temporal Reasoning};
        \node [subpart, below=0.2 of geom.south west, anchor=north west] (world-update) {Sensors fusion};
        \node [subpart, right=0.2 of world-update] (geom-model) {Geometric model of the environment};
        \node [subpart, right=0.2 of geom-model] (fact-prod) {Symbolic facts production};
      \end{tikzpicture}
    };

  %%% MHP
  \node at (9,0)[skill, fill=BurntOrange!50] (mhp) {Human-aware \\ Motion and Manipulation \\ Planning};

  %%% Relations between components
  \path (shary.340) edge [<->, bend left] node[label] {motion plan \\ requests} (mhp);
  \path (shary.west) edge [<->, bend right] node[label] {shared \\ plans} (hatp);
  \path (hatp) edge [<->, bend right] node[label] {world model and \\ agents beliefs} (oro.170);
  \path (dialogs) edge [<->, bend left] node[label] {natural language \\ grounding} (oro.190);
  \path (spark.100) edge [->, bend right] node[label] {symbolic \\ facts} (oro);
  \path (shary) edge [<->, bend left] node[label] {Events, \\ World model and \\ agents beliefs} (oro);
  \path (shary) edge [<->, bend left] node[label] {action monitoring \\ and management of \\ position hypotheses} (spark);
  \path (lowlevel) edge [->] (spark);
  \path (lowlevel.east) edge [<-, bend right=80, looseness=1.2] (shary.east);

This architecture moves away from standard layered approaches found in
robotics~\cite{Gat1998three, Volpe2001CLARAty, Goldberg2002}. Interactions
between components at the deliberative level are mostly bidirectional and we do
not introduce layers of abstraction amongst software components\footnote{We do
have lower-level modules to execute actions or manage sensors, but all
cognition-related modules reside at the same level.}. Dialogue processing, for
instance, illustrates this structure: This component does not simply act as an
alternative perceptual input to the symbolic database; it also
actively queries previously acquired knowledge to disambiguate and validate the
newly created symbolic knowledge (see section~\ref{sect|com}).

Our architecture relates to \emph{Beliefs, Desires, Intentions} (BDI)
architectures. BDI architectures are primarily focused on \emph{practical
reasoning}, \ie the process of deciding, step by step, which action to perform
to reach a goal (as summarized by Woolridge~\cite{Woolridge1999}). The
management of the interaction between knowledge (the beliefs) and task and plan
representation and execution (the desires and the intentions) is central, and
aims at selecting at each step the best subgoal. It becomes then an intention
that the robot commits to.

This interaction between knowledge and actions is also central to our approach
(as for any cognitive system): it is one amongst all the activities carried by
the robot, actually performed by the communication components (that acquire
desires from interaction with agents) and the execution controller that may
decide to take an incoming desire into account to create its own internal
goals. The controller generates and manages intentions from these goals with
the help of a symbolic task planner, that also has direct access to the
knowledge base.

This activity is however not the backbone of our architecture. Other
activities are conducted in parallel, without being explicitly considered as
desires: assessment of the situation and the environment, dialogue (including
performative dialogue that can possibly change the internal state of the robot,
but does not lead directly to the creation of desires, like statement assertion or
question answering), various background monitoring and recognition tasks, etc.

\subsection{A Knowledge model}

In this architecture, knowledge manipulation relies on a
semantic \emph{blackboard}: a central server (the {\sc Oro}
server~\cite{Lemaignan2010}) stores knowledge as it is produced by each of the
deliberative components. It conversely exposes a {\tt json}-based RPC
API~\cite{lemaignan2012kbapi} to query the knowledge base.

Knowledge is represented as RDF triples in the OWL sub-language. Each
time triples are added or removed from the knowledge base, a Description
Logics reasoner ({\sc Pellet}\footnote{\tt http://clarkparsia.com/pellet/})
classifies the whole ontology and inserts all possible inferred triples.

At any time, the knowledge available to the robot may come from three sources:
{\it a priori} knowledge is stored in an ontology (the {\sc OpenRobots Ontology}),
loaded when the robot initializes. This static source covers the
\emph{common-sense} knowledge of the robot, and optionally some
scenario-specific knowledge (for instance about objects that are to be
manipulated). The second part of the knowledge is acquired at runtime from
perception, interaction, decision making.  We go over the processes it involves
in the next sections. Lastly, the third source of knowledge is the output of the
reasoner.

Contrary to other projects like KnowRob~\cite{Tenorth2009a} that have introduced
the concept of \emph{computables} to lazily evaluate/acquire symbolic facts when
needed, we have an \emph{explicit} approach where we greedly compute and assert
symbolic statements (like spatial relations between objects, see
Section~\ref{sect|sit-ass}). This design choice trades scalability for explicit
reasoning: at any time, the full belief state is explicitely stated, and
provides the reasoner with the largest possible inference domain. This is of
special importance for an \emph{event-based} architecture (see
Section~\ref{sect|ctrl}), where, by definition, we do not know beforehand what
we are ``looking for'', and we prefer instead greedly infer as much as possible
to build a belief state as comprehensive as possible.

@@

\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
    >=latex,
    every edge/.style={<-, draw, very thick},
    every node/.style={draw, font=\sf, node distance=0.5, rounded corners,
align=center, inner sep=5pt,fill=LimeGreen!50}]

@@

This leads to a bidirectional design process: from \emph{bottom-up} regarding
the choices of concepts to model, \emph{top-down} regarding the upper part of the
taxonomy. This upper part of the ontology is pictured on
Figure~\ref{fig|upper_tbox}. All the classes visible in this figure belong to the
{\sc OpenCyc} namespace (the {\tt cyc:} prefix is omitted for clarity).

Aligning the upper part of the ontology on {\sc OpenCyc} (as done by other
KRS, like {\sc KnowRob}~\cite{Tenorth2009a} or PEIS K\&R~\cite{Daoutis2009})
has multiple advantages. First the design of this part of the ontology is
generally difficult: it pertains to abstract concepts whose mutual relations
comes to philosophical debates. The upper taxonomy of {\sc OpenCyc} represents
a relative consensus, at least within the semantic Web community. Then, because
it is a well established project with numerous links to other on-line databases
(like Wikipedia or WordNet), the reuse of important {\sc OpenCyc} concepts
ensures to a certain extend that the knowledge stored by the robot can be
shared or extended with well-defined semantics. A good example is the concept
of \emph{Object}: In everyday conversation, an object is a relatively small
physical thing, that can be typically manipulated. Normally, a human is not
considered as an object. In {\sc Cyc}, an object has a more precise definition:
it is something \emph{partially tangible}. That includes obviously the humans,
and actually many other entities that would not be commonly said to be objects
(the Earth for instance). Thus the importance of relying on well-defined and
standard semantics to exchange informations between artificial systems.

Figure~\ref{fig|upper_tbox} also illustrates the fundamental disjunction
in the ORO model between \emph{temporal} and \emph{spatial} entities (formally,
$(TemporalThing \sqcap SpatialThing)^{\mathcal{I}} = \emptyset$, with
$\mathcal{I}$ the \emph{interpretation} of our model).

The class \concept{purposeful action} is the superset of all the actions that
are voluntarily performed by the robot (or another agent). Subclasses (like
\concept{Give}, \concept{LookAt}, etc.) are not asserted in the common-sense
ontology, but are added by the execution controller (in link with the symbolic
task planner) and the natural language processor based on what is actually
performable and/or understandable by the robot at run-time.

The tree in Figure~\ref{fig|upper_tbox} (this subset of the ontology is indeed
a tree: this has however not to be the case in general, and, as a matter of
fact, the TBox of the whole ORO common-sense ontology does not form a tree) is
not equally developed at lower levels. We have already briefly mentioned the
developments of the actions. The other important part is the descendants of the
\concept{partially tangible thing} (what is commonly called an \emph{object}).
Figure~\ref{fig|tangible_things_tbox} gives more details on this part of the
ontology.

@@

\resizebox{0.7\textwidth}{!}{%
\begin{tikzpicture}[
    >=latex,
    every edge/.style={<-, draw, very thick},
    every node/.style={draw, font=\sf, node distance=0.5, rounded corners,
align=center, inner sep=5pt,fill=BurntOrange!50}]

@@

\end{tikzpicture}
}
    \caption{TBox of the specialisations of \concept{PartiallyTangible}.}
    \label{fig|tangible_things_tbox}
\end{figure}

This excerpt from the ontology makes the bottom-up design process visible: only
few types of \emph{partially tangible} things appear, and only subclasses
relevant to the context of service robotics in an human-like environment are
present. For performances and ease of use, we do not attempt to comprehensively
cover the field. We opportunistically extend the common-sense knowledge when
required by experiments.

Lastly, the ORO common-sense ontology contains several rules and class
expressions that encode non-trivial inferences.

The definition of the \concept{Bottle} is a typical example:

@@

If a human informs the robot that a given object is indeed a bottle, the robot
can then infer much more on this object. And if the human affirms that a car is
a bottle, the robot may question this assertion because of the inconsistent
size.

We discuss in section~\ref{krs-discussion} the strengths and weaknesses of our
knowledge framework.

\subsection{Internal cognitive processes}
\label{sect|intern}

@@

Our other controller, {\sc Shary}, relies on the symbolic task planner to
generate at runtime suitable sets of atomic actions.

\begin{table}
\begin{center}
\begin{tabular}{p{8cm}}
\hline
    {\bf Manipulation} \\
     {\tt attachobject}, {\tt basicgive}, {\tt basictake}, {\tt close\_gripper}, {\tt configure\_grippers}, {\tt grab\_gripper}, {\tt handover}, {\tt hide}, {\tt open\_gripper}, {\tt pick}, {\tt put}, {\tt put\_accessible}, {\tt release\_gripper}, {\tt show}, {\tt take} \\
\hline
    {\bf Gaze control} \\
     {\tt glance\_to}, {\tt look\_at}, {\tt sweep}, {\tt switch\_active\_stereo\_pair}, {\tt track}, {\tt cancel\_track} \\
\hline
    {\bf Navigation} \\
     {\tt carry}, {\tt follow}, {\tt cancel\_follow}, {\tt goto}, {\tt moveclose}, {\tt waypoints} \\
\hline
    {\bf Local navigation} \\
     {\tt dock}, {\tt rotate}, {\tt translate} \\
\hline
    {\bf Posture configuration} \\
     {\tt extractpose}, {\tt idle}, {\tt manipose}, {\tt movearm}, {\tt rest}, {\tt setpose}, {\tt settorso}, {\tt tuckedpose} \\
\hline
\end{tabular}
\end{center}
\caption{Main {\sc pyRobots} \emph{actions}, sorted by categories. These
actions are combined at runtime into higher-level \emph{tasks}.}

@@

\subsection{\emph{Moving to London} scenario}

>>>>

\usepackage{amsmath} % \text

@@

\section{Deliberative Architecture and Knowledge Model}

\begin{figure*}[ht]
\centering

  %%% ORO
    \node at (0,0)[skill, ultra thick, fill=LimeGreen!50] (oro) {{\sc Oro} -- Symbolic facts \\ and beliefs management};

  %%% HATP
  \node at (-6, 2)[skill, fill=PineGreen!50] (hatp) {HATP -- Human-aware \\ symbolic task planning};

  %%% DIALOGS
  \node at (-6, -2) [skill, fill=BrickRed!50] (dialogs) {{\sc Dialogs} \\ Dialogue processing};

  %%% SPARK
  \node at (4,-3)[skill, fill=Purple!50] (spark) {%
      \begin{tikzpicture}
          \node at (0,0) (geom) {{\sc Spark} -- Geometric \& Temporal Reasoning};
        \node [subpart, below=0.2 of geom.south west, anchor=north west] (world-update) {Sensors fusion};
        \node [subpart, right=0.2 of world-update] (geom-model) {Geometric model of the environment};
        \node [subpart, right=0.2 of geom-model] (fact-prod) {Symbolic facts production};
      \end{tikzpicture}
    };

  %%% MHP
    \node at (9,0)[skill, fill=BurntOrange!50] (mhp) {{\sc mhp} -- Human-aware \\ Motion and Manipulation \\ Planning};

  %%% Relations between components
  \path (shary.340) edge [<->, bend left] node[label] {motion plan \\ requests} (mhp);
  \path (shary.west) edge [<->, bend right] node[label] {shared \\ plans} (hatp);
  \path (hatp) edge [<->, bend right] node[label] {world model and \\ agents beliefs} (oro.170);
  \path (dialogs) edge [<->, bend left] node[label] {natural language \\ grounding} (oro.190);
  \path (spark.100) edge [->, bend right] node[label] {symbolic \\ facts} (oro);
  \path (shary) edge [<->, bend left] node[label] {events, \\ world model and \\ agents beliefs} (oro);
  \path (shary) edge [<->, bend left] node[label] {action monitoring \\ and management of \\ position hypotheses} (spark);
  \path (lowlevel) edge [->] (spark);
  \path (lowlevel.east) edge [<-, bend right=80, looseness=1.2] (shary.east);

@@

Figure~\ref{fig|archi} gives an overview of our architecture. An active
knowledge base ({\sc Oro}), conveniently thought as a \emph{semantic
blackboard}, connects most of the modules together: the \emph{geometric
reasoning} module (called {\sc Spark}) produces symbolic assertions (like
\stmt{BOOK1 isOn TABLE}) describing the state and dynamics of the robot's
environment. These logical statements are stored in the knowledge base, and
reused by the language processing module ({\sc Dialogs}), the symbolic task
planner (HATP) and the execution controller. The output of the language
processing module, or the activities started by the robot controller are
likewise stored as symbolic statements.

For instance, when processing a sentence like ``give me another book'', the {\sc
Dialogs} module sends at some point a request to the knowledge base that looks
like {\tt \footnotesize find(?book type Book, ?book differentFrom
BOOK1)}\footnote{We present a similar but complete example at
section~\ref{moving-london}.} and may write back assertions like \stmt{HUMAN
desires GIVE\_ACTION45, GIVE\_ACTION45 actsOn BOOK2} to {\sc Oro}. The HATP
planner then uses the knowledge base to initialize the planning domains with
similar requests ({\tt \footnotesize find(BOOK2 isAt ?location)}, etc.). The
execution controller typically monitor conditions (by subscribing to events
like: {\tt \footnotesize onNewMatch(HUMAN desires ?goal)}) and stores what the
robot is currently doing (\stmt{myself currentlyPerforms GIVE\_ACTION45}).

To some extend, this architecture moves away from classical layered approaches
found in robotics~\cite{Gat1998three, Volpe2001CLARAty, Goldberg2002}.
Interactions between components at the deliberative level are mostly
bidirectional and we do not introduce layers of abstraction amongst software
components\footnote{We do have lower-level modules to execute actions or manage
sensors, but all cognition-related modules live in the same global deliberative
layer.}. Dialogue processing, for instance, illustrates this structure. This
component does not purely act as an alternative sensing modality that would be
fed to a distinct deliberative component: on the contrary, it actively queries
the knowledge base to interpret and disambiguate natural language, and in that
regards, it is fully integrated to the deliberative process itself (we detail
natural language processing at section~\ref{sect|com}).

Our architecture however relates to \emph{Beliefs, Desires, Intentions} (BDI)
architectures. As put by Woolridge~\cite{Woolridge1999}, BDI architectures are
primarily focused on \emph{practical reasoning}, \ie the process of deciding,
step by step, which action to perform to reach a goal. The management of the
interaction between knowledge (the beliefs) and task and plan representation and
execution (the desires and the intentions) is central, and aims at selecting at
each step the best subgoal. It becomes then an intention that the robot commits
to.

As for any cognitive system, this fundamental interaction between knowledge and
actions is central to our approach, and involves the dialogue component that
acquires \emph{desires} from the other agents, the planner and the execution
controller that may first decide to take or not into account an incoming desire
as a \emph{goal}, and then generates and manages \emph{intentions} from these
goals with the help of a symbolic task planner.

Other activities are however conducted in parallel, without being explicitly
triggered by \emph{desires} in the BDI sense, like situation assessment and
monitoring or other forms of dialogue (including performative dialogue that can
possibly change the internal state of the robot, but does not lead directly to
the creation of \emph{desires}, like assertion of new facts or question
answering).

\subsection{Knowledge Model}

In our architecture, knowledge manipulation relies on a central server (the {\sc
Oro} server~\cite{Lemaignan2010}, Figure~\ref{fig|spark-oro} top) which stores
knowledge as it is produced by each of the deliberative components. It
conversely exposes a {\tt json}-based RPC API~\cite{lemaignan2012kbapi} to query
the knowledge base.  We represent knowledge as RDF triples in the OWL
sub-language. Each time triples are added or removed from the knowledge base, a
Description Logics reasoner ({\sc Pellet}\footnote{\tt
http://clarkparsia.com/pellet/}) classifies the whole ontology and inserts all
possible inferred triples.

This architecture design (a central knowledge base that essentially appears as a
passive component to the rest of the system -- even though it actually actively
processes the knowledge pool in the background, for instance with the reasoner)
departs from other approaches like the CAST model~\cite{Hawes2007} where
knowledge is represented as a diffuse resource, or the CRAM/KnowRob
architecture~\cite{Beetz2010} where the knowledge base is an active hub that
pro-actively queries perceptual components to acquire knowledge. We believe that
our design leads to a good \emph{observability} (knowledge flows are explicit
and easy to capture since they are centralized) as well as high modularity
(modules communicate through a defined and unified API).

At run-time, the knowledge available to the robot at a given time comes from
three sources. {\it A priori} knowledge is stored in an ontology (the {\sc
OpenRobots} ontology, discussed below) and loaded at startup. This static source covers the
\emph{common-sense} knowledge of the robot, and optionally some
scenario-specific knowledge (for instance, about objects that are to be
manipulated). The second part of the knowledge is acquired at run-time from
perception, interaction and planning. The next sections detail these processes.
Lastly, the third source of symbolic statements is the reasoner itself.

Contrary to other projects like KnowRob~\cite{Tenorth2009a} that relies on
the concept of \emph{computables} to lazily evaluate/acquire symbolic facts when
needed, we have an \emph{explicit} approach where we greedly compute and assert
symbolic statements (like spatial relations between objects, see
Section~\ref{sect|sit-ass}). This design choice trades scalability for explicit
reasoning: at any time, the full belief state is explicitely stated, and
provides the reasoner with the largest possible inference domain. This is of
special importance for an \emph{event-based} architecture like ours (see
Section~\ref{sect|ctrl}), where, by definition, we do not know beforehand what
we are ``looking for'', and we need instead greedly infer as much as possible
to build a belief state as comprehensive as possible.

@@

\resizebox{0.8\textwidth}{!}{%
\begin{tikzpicture}[
    >=latex,
    every edge/.style={<-, draw, very thick},
    every node/.style={draw, font=\sf, node distance=0.5, rounded corners,
align=center, inner sep=5pt,fill=LimeGreen!50}]

@@

This leads to a bidirectional design process: from \emph{bottom-up} regarding
the choices of concepts to model, \emph{top-down} regarding the upper part of
the taxonomy. This upper part of the ontology is pictured on
Figure~\ref{fig|upper_tbox}. All the classes visible in this figure belong to
the {\sc OpenCyc} namespace.

Aligning the upper part of the ontology on {\sc OpenCyc} (as done by other
knowledge representation systems, like {\sc KnowRob}~\cite{Tenorth2009a} or PEIS
K\&R~\cite{Daoutis2009}) has multiple advantages. First the design of this part
of the ontology is generally difficult: it pertains to abstract concepts whose
mutual relations comes to philosophical debates. The upper taxonomy of {\sc
OpenCyc} represents a relative consensus, at least within the semantic Web
community. Then, because it is a well established project with numerous links to
other on-line databases (like Wikipedia or WordNet), the reuse of important {\sc
OpenCyc} concepts ensures to a certain extend that the knowledge stored by the
robot can be shared or extended with well-defined semantics. A good example is
the concept of \emph{Object}: In everyday conversation, an object is a
relatively small physical thing, that can be typically manipulated. Normally, a
human is not considered as an object. In {\sc Cyc}, an object has a more precise
definition: it is something \emph{partially tangible}. That includes obviously
the humans, and actually many other entities that would not be commonly said to
be objects (the Earth for instance). Thus the importance of relying on
well-defined and standard semantics to exchange informations between artificial
systems.

Figure~\ref{fig|upper_tbox} also illustrates the fundamental disjunction
in the ORO model between \emph{temporal} and \emph{spatial} entities (formally,
$(\text{TemporalThing} \sqcap \text{SpatialThing})^{\mathcal{I}} = \emptyset$, with
$\mathcal{I}$ the \emph{interpretation} of our model).

The class \concept{PurposefulAction} is the superset of all the actions that are
voluntarily performed by the robot (or another agent). Actual actions (\ie
subclasses of \concept{PurposefulAction} like \concept{Give} or
\concept{LookAt}) are not initially asserted in the common-sense ontology. They
are instead added at run-time by the execution controller (in link with the
symbolic task planner) and the natural language processor based on what is
actually performable and/or understandable in the scenario context (\ie the
current robot configuration and the actions required by the scenario).

The tree in Figure~\ref{fig|upper_tbox}\footnote{This subset of the ontology is
indeed a tree. This has however not to be the case in general, and, as a matter
of fact, the TBox of the whole ORO common-sense ontology does not form a tree}
is not equally developed in each directions at lower levels. The descendants of
\concept{PartiallyTangibleThing} (\ie what we commonly call \emph{objects}), for
instance, are pictured in Figure~\ref{fig|tangible_things_tbox}. This excerpt
from the ontology makes the bottom-up design process clear: only few types of
\emph{partially tangible} things appear, and those are only subclasses relevant
to the context of service robotics in an human-like environment. For performance
reasons as well as clarity, we do not attempt to proactively extend the
conceptual coverage of the field. We instead opportunistically extend the
common-sense knowledge when required by experiments.

@@

\resizebox{0.5\textwidth}{!}{%
\begin{tikzpicture}[
    >=latex,
    every edge/.style={<-, draw, very thick},
    every node/.style={draw, font=\sf, node distance=0.5, rounded corners,
align=center, inner sep=5pt,fill=BurntOrange!50}]

@@

\end{tikzpicture}
}
    \caption{TBox of the specialisations of \concept{PartiallyTangibleThing}.}
    \label{fig|tangible_things_tbox}
\end{figure}

Lastly, the ORO common-sense ontology contains several rules and class
expressions that encode non-trivial inferences. The definition of
\concept{Bottle} as found in the ORO ontology is a typical example:

@@

If a human informs the robot that a given object is indeed a bottle, the robot
can then derive a few more informations on this object. And, conversely, if the
human affirms that a car is a bottle, the robot may question this assertion
because of the inconsistent size (the {\sc Dialogs} module relies on such
logical consistency checks when processing natural language inputs, both to
ensure that the verbal input has been correctly acquired and to verify that what
the human says does actually make sense).

We will come back and discuss in section~\ref{krs-discussion} the strengths and
weaknesses of this knowledge framework.

\subsection{Internal Cognitive Processes}
\label{sect|intern}

\subsubsection{Symbolic Anchoring}

@@

Our other controller, {\sc Shary}, relies on the symbolic task planner to
generate at run-time suitable sets of atomic actions.

\begin{table}
\begin{center}
\begin{tabular}{p{8cm}}
\hline
    {\bf Manipulation} \\
     {\tt attachobject}, {\tt basicgive}, {\tt basictake}, {\tt close\_gripper}, {\tt configure\_grippers}, {\tt grab\_gripper}, {\tt handover}, {\tt hide}, {\tt open\_gripper}, {\tt pick}, {\tt put}, {\tt put\_accessible}, {\tt release\_gripper}, {\tt show}, {\tt take} \\
\hline
    {\bf Gaze control} \\
     {\tt glance\_to}, {\tt look\_at}, {\tt sweep}, {\tt switch\_active\_stereo\_pair}, {\tt track}, {\tt cancel\_track} \\
\hline
    {\bf Navigation} \\
     {\tt carry}, {\tt follow}, {\tt cancel\_follow}, {\tt goto}, {\tt moveclose}, {\tt waypoints} \\
\hline
    {\bf Local navigation} \\
     {\tt dock}, {\tt rotate}, {\tt translate} \\
\hline
    {\bf Posture configuration} \\
     {\tt extractpose}, {\tt idle}, {\tt manipose}, {\tt movearm}, {\tt rest}, {\tt setpose}, {\tt settorso}, {\tt tuckedpose} \\
\hline
\end{tabular}
\end{center}
\caption{Main {\sc pyRobots} \emph{actions}, sorted by categories. These
actions are combined at run-time into higher-level \emph{tasks}.}

@@

\subsection{\emph{Moving to London} scenario}
\label{moving-london}
